---
title: "Data Import"
output: github_document
---

```{r setup, echo = FALSE, message = FALSE}
library(tidyverse)
```

This document will show how to import data. 

## Import the FAS Litters CSV
###Notes about paths: We should use relative paths instead of absolute paths because this makes a project more easily reproducible from any computer, not just the original machine. I am using relative paths in this document. Notice that I haven't installed the entire janitor package, but I want to be able to use the clean_names function. I can use this style code to pull just this specific command. 

```{r}
litters_df = read_csv("data/FAS_litters.csv")

litters_df = janitor::clean_names(litters_df)
```

## Look at the dataset

```{r}
litters_df
head(litters_df)
tail(litters_df)
```

```{r eval = FALSE}
view(litters_df)
```

##Learning assessment

Use relative paths
```{r, eval = FALSE}
pups_df = read_csv("data/FAS_pups.csv")

pups_df = janitor::clean_names(pups_df)
```

##Look at read_csv options
Skip can be used to skip first few rows, in case people have added unnecessary information there
```{r}
litters_df=
  read_csv(
    file = "data/FAS_litters.csv",
    skip = 1 
  )
```

What about missing data? Here is a quick way to make missing values uniform in your dataset. 

```{r}
litters_df=
  read_csv(
    file = "data/FAS_litters.csv",
    na = c("NA", "", ".")
  )
```

What if we code 'group' as a factor variable?

```{r}
litters_df = 
  litters_df=
  read_csv(
    file = "data/FAS_litters.csv",
    na = c("NA", "", "."), 
    col_types = cols(
      Group = col_factor()
    )
)
```

